\subsection{Transitioning SmartLock from Prototype to Market-Ready Product}

To move from a functional prototype to a marketable SmartLock product, several key engineering and business steps need to be addressed. This involves refining both hardware and software components, ensuring scalability and security standards.

\subsubsection{Custom Hardware Design}

The ESP32 microcontroller used in the prototype provides an platform for development and proposal, but a custom-designed microcontroller will offer improved performance, cost-efficiency, power-efficiency, and security.

\begin{itemize}
  \item \textbf{PCB Design:} Develop a custom printed circuit board (PCB) integrating a microcontroller with essential peripherals (e.g., motor drivers, Wi-Fi/Bluetooth module, battery management).
  \item \textbf{Power Optimization:} Ensure low-power operation modes and efficient battery usage for real-world longevity.
  \item \textbf{Form Factor:} Design a compact form to fit lock, pin-pad, microcontroller dimensions and installation constraints.
  \item \textbf{Manufacturability:} Optimize for scalable manufacturing, component sourcing, manufacture, and assembly.
\end{itemize}

\subsubsection{Backend Infrastructure Development}

Firestore offers an accurate prototype, but a production system needs more control, security, and scalability.

\begin{itemize}
  \item \textbf{Cloud-Based Database:} Develop a backend using platforms such as AWS, Azure solution with REST/GraphQL APIs.
  \item \textbf{Security Architecture:} Implement end-to-end encryption, secure authentication, and role-based access control.
  \item \textbf{Real-Time Communication:} Use MQTT or WebSockets for real-time lock state updates.
\end{itemize}

\subsubsection{Mobile/Web App Enhancement}

The current web interface can be transformed into a polished, user-friendly app for mainstream adoption.

\begin{itemize}
  \item \textbf{Cross-Platform Support:} Build using Flutter, React Native, or Swift/Kotlin for Android and iOS platforms.
  \item \textbf{User Experience (UX):} Incorporate intuitive design, user onboarding, remote lock/unlock, and notification features.
\end{itemize}

\subsubsection{Compliance and Security Certification}

A production-ready smartlock must comply with legal standards and certifications.

\begin{itemize}
  \item \textbf{Certifications:} Obtain CE, FCC, or other regional certifications for wireless and electronic devices.
  \item \textbf{Privacy Compliance:} Ensure GDPR/CCPA compliance with respect to user data handling and storage.
\end{itemize}


