\newpage

\section{Design}

\begin{comment}
 What is required for the Design Section:
 - Aesthetic Prototype ( CAD Images, photos of physical prototypes, drawings )
 - Design for Manufacture, Assembly, Maintenance
 - Block Diagrams
 - Wiring Diagrams
 - State Transition Diagrams
 - Technology ( languages, hardware, etc. )
 - Simulation
 - Modeling
\end{comment}

\subsection{Aesthetic Prototype} % Neena will input the images here

\subsection{Design for Manufacture, Assembly, Maintenance} % we need to add more detail from our previous work from 123A...read his comments from draft

\subsection{Block Diagrams}

\subsection{Wiring Diagrams}

\subsection{State Transition Diagrams}

\subsection{Technology}
For our hardware components, we used the ESP32-C3 microcontroller, programmed in C++ using the Arduino IDE. To support our development, we integrated several key libraries: Firebase Client by Mobizt, ArduinoJson by Benoit Blanchon, WiFiManager by tzapu, and Keypad by Mark Stanley and Alexander Brevig. These libraries enabled reliable communication with our Firebase server, interfacing with the keypad for user input, and creating a Wi-Fi access point for initial smart lock configuration. 

As for the smartphone app, we used Swift with Xcode for development. This means that our application currently builds natively for iOS devices only, such as iPhones and iPads. The app allows users to unlock and lock the smart lock remotely, receive battery and connectivity status notifications, and manage temporary PIN codes.

While our current version supports iOS exclusively, we plan to explore cross-platform solutions such as Flutter or React Native in the future to make the app available on Android devices as well. This would broaden accessibility and improve compatibility for a wider range of users.

\subsection{Simulation}

\subsection{Modeling}

