\subsection{\textcolor{gray}{Executive Summary}}

In an era where security and convenience are necessary, traditional lock-and-key systems are becoming outdated. Lost keys, forgotten access codes, and lack of remote control present serious challenges for homeowners and businesses alike. Our Auto Smart Lock project is a solution designed to enhance security while offering friendly user accessibility.
\newline
Our goal is to develop a smart lock that integrates modern authentication methods with remote access capabilities. By leveraging an ESP32-C3 microcontroller in conjunction with Firebase cloud services, our smart lock enables users to lock and unlock their doors from anywhere, eliminating the risks associated with traditional keys.
\newline

At the core of our smart lock is an ESP32-C3 microcontroller, which connects to WiFi and Firebase cloud services to securely manage lock and unlock commands. When a user enters a PIN or sends a command from their phone, the system checks if the code is valid. If it is, the solenoid lock is triggered, unlocking the door. We’ve designed the lock to be fast, secure, and easy to install, with a 3D-printed casing to house the components.
\newline

Before finalizing the prototype, we are running key tests to ensure everything works smoothly. These tests check if the phone properly connects to the lock, if the lock responds quickly, if multiple users can access it without conflicts, and if temporary PINs expire when they should. Our next steps include assembling all parts, optimizing performance, and making sure the system is fully secure and reliable. By the end of Winter 2025, we aim to have a fully functional smart lock prototype that provides a safer, smarter, and more convenient way to secure homes.