\newpage % new section requiring new page

\section{Features For Future Versions}

In future versions of our smart lock system, our team aims to introduce several new features to enhance reliability, usability, and security. These improvements are based on user feedback, system testing, and design reviews.

\begin{comment}
    - Lock has a hole for a physical key to unlock door for emergency emergency case!
    - Make bluetooth an option to open the door, without clicking the lock and unlock button.
    - Sending notifications about battery health when door lock is low battery
    - Send notifications about the lock having no network
    - Implementing a more secure algorithm for the input pin
\end{comment}

\subsection{Smart Lock Hardware Improvements}

\begin{itemize}
    \item \textbf{Physical Key Backup:}  
    To handle worst-case scenarios where the battery is fully drained, we plan to include a mechanical keyhole for emergency manual unlocking.

    \item \textbf{Tamper Detection:}  
    The smart lock will include tamper detection sensors that trigger an alert if physical interference or forced entry is detected. When tampering is detected, the system will notify the owner through the app and optionally sound an audible alarm to deter intruders.

    \item \textbf{Rechargeable Battery with USB-C Port:}  
    Future versions of the smart lock will feature a built-in rechargeable battery that can be conveniently charged using a standard USB-C port. This eliminates the need for disposable batteries, reducing waste and providing a more sustainable and user-friendly power solution.
\end{itemize}


\subsection{Smartphone App Enhancements}

\begin{itemize}
    \item \textbf{Proximity-Based Unlocking:}  
    Users will be able to automatically unlock the door when in close range of the smart lock, eliminating the need to manually press the unlock button. This feature will require the app to remain running in the background.

    \item \textbf{Battery Health Notifications:}  
    When the smart lock’s battery drops below 20\%, the app will notify the user with a reminder to replace or recharge the battery.

    \item \textbf{Network Connectivity Alerts:}  
    The app will notify the user if the lock goes offline or reconnects to Wi-Fi. This helps users understand when remote control or cloud-based PIN codes may be unavailable.

    \item \textbf{Secure PIN Code Generation:}  
    Future versions will use cryptographically secure random number generators to produce unpredictable PIN codes. Generated PINs will avoid repeated digits and common patterns to enhance protection against brute-force guessing.

    \item \textbf{Guest PIN Expiry:}  
    Owners can assign a PIN with a specific expiration time. Once expired, the PIN will be automatically deactivated and removed from the list of valid access codes, preventing any further use.

\end{itemize}
