\newpage
\section{Installation}

\subsection{Phone App Installation}
Open up the pamphlet included with the smart lock system. Inside, you will find a QR code labeled "App Download." Using your smartphone, scan the QR code to be redirected Google Play or Apple App Store.

Once the page loads:
\begin{enumerate}
    \item Tap \textbf{Download} or \textbf{Install}.
    \item After installation is complete, open the app.
    \item Create an account using your email and a secure password, or log in if you already have an account.
    \item Grant the necessary permissions for Bluetooth and Location if prompted.
\end{enumerate}

The app is now ready to pair with your smart lock.

\subsection{Smart Lock Installation}
Follow these steps to install the smart lock on your door:

\begin{enumerate}
    \item Remove the existing lock hardware from your door.
    \item Align the provided smart lock mounting plate with the existing holes and secure it using the included screws and screwdriver.
    \item Attach the smart lock unit onto the mounting plate. Ensure all connections are secure and the lock is properly aligned.
    \item Insert the provided batteries into the battery compartment. The device should power on automatically.
    \item Open the mobile app, go to the \textbf{Devices} section, and tap \textbf{Add New Lock}.
    \item Follow the on-screen instructions to pair the lock with your phone via Bluetooth or Wi-Fi.
    \item Once paired, test the lock by tapping the \textbf{Lock} and \textbf{Unlock} buttons within the app.
\end{enumerate}

Your smart lock is now installed and ready for use. Refer to the Troubleshooting section if you encounter any issues during setup.

\subsection{Troubleshooting}

If you experience issues during installation, refer to the common problems and solutions below:

\begin{itemize}
    \item \textbf{App not installing:}  
    Ensure your device has a stable internet connection and sufficient storage space. If the problem persists, restart your device and try again.

    \item \textbf{Unable to scan QR code:}  
    Check that your camera is focused and clean. If scanning still fails, manually search for the app by name, "Smart Lock", in your device’s app store.

    \item \textbf{Cannot create or log into account:}  
    Double-check that your email is entered correctly and that your password meets the required complexity. Try resetting your password if needed.

    \item \textbf{Smart lock not turning on:}  
    Ensure the batteries are inserted correctly and are fully charged. Replace the batteries if necessary.

    \item \textbf{App cannot find the smart lock:}  
    Make sure Bluetooth and Location services are enabled on your phone. Move closer to the lock and try again. Restart the app and the lock if necessary.

    \item \textbf{Lock not responding to commands from the app:}  
    Confirm that the lock is still paired with your device and connected via Bluetooth or Wi-Fi. If not, re-pair the lock through the app’s device settings.

    \item \textbf{Physical installation issues:}  
    Ensure that all screws are tightened and that the lock is not misaligned. Refer to the diagram in the pamphlet for proper mounting.

    \item \textbf{Device shows as "Offline" in app:}  
    Check your internet connection and ensure the smart lock is within range of your Wi-Fi network. Reboot the lock and router if needed.

    \item \textbf{Device arrived broken:}  
    If the smart lock or any components appear physically damaged upon unboxing, do not attempt installation. Contact customer support immediately using the information provided in the pamphlet or within the mobile app. Be prepared to provide your order number, a description of the issue, and photos of the damage to expedite the replacement process.

\end{itemize}

If problems persist, please refer to the full user manual or contact technical support through the app’s Help section.
