\newpage

\section{Introduction}

\begin{comment}
 What is required for Introduction:
 - Need & Goal statement
 - Personas
 - Research into existing designs / products that meet / partially meet the need
 - Sustainability Statement
\end{comment}

%% Need & Goal Statement %%

\subsection{Need \& Goal Statements}
\begin{itemize}
    \item Need Statement - Homeowners need a safe, reliable smart lock they can control from their phone—for everyday use, granting access to temporary guests, and ensuring secure entry even when Wi-Fi is unavailable.
    
    \item Goal Statement - Design and build a smart lock that offers secure smartphone control, supports one-time PINs for temporary access, and ensures offline entry through emergency codes, providing homeowners with reliable, convenient access in all conditions.
\end{itemize}

%% Personas %%

\subsection{Persona 1: Marcus Lee}

\begin{itemize}
    \item \textbf{Background:} Homeowner, 42 years old, IT Manager, lives in a suburban neighborhood.
    \item \textbf{Goals:} 
    \begin{itemize}
        \item Secure keyless entry for his family
        \item Enable remote monitoring when traveling
        \item Integrate smart lock with his existing smart home system
    \end{itemize}
    \item \textbf{Behaviors:}
    \begin{itemize}
        \item Uses smart home apps
        \item Values reliability and ease of setup over complex features
    \end{itemize}
    \item \textbf{Traits:} Security-conscious, tech-savvy, efficiency-driven
\end{itemize}

\subsection{Persona 2: Sophia Nguyen}

\begin{itemize}
    \item \textbf{Background:} 35 years old, owns and manages multiple Airbnb properties.
    \item \textbf{Goals:}
    \begin{itemize}
        \item Simplify guest access
        \item Automate key management
        \item Track entries remotely
    \end{itemize}
    \item \textbf{Behaviors:}
    \begin{itemize}
        \item Regularly updates access codes
        \item Prefers integration with rental management software
        \item Needs a user-friendly app with remote access and activity tracking
    \end{itemize}
    \item \textbf{Traits:} Business-oriented, customer-focused, convenience-driven
\end{itemize}

%% Research into existing designs and/or products that meet / partially meet the need %%

\subsection{Existing designs partially meeting the requirements}
There are several existing designs that partially meets the requirement of what we want. We will list out each of the product and explain about what it has and why it did not meet our expectation.

\begin{enumerate}
    \item \href{https://www.amazon.com/August-Home-Connected-Electronic-%E2%80%8EAUG-SL05-M01-S01/dp/B082VXK9CK?th=1}{August Home}. This product has the ability to control the lock using a phone, can open the door for guest using phone. However the product does not have the ability to provide pin codes to guests say for a period of time.
    \item \href{https://a.co/d/3ruDPmO}{Schlage Encode Smart WiFi Deadbolt Lock for Front Door}. This product has a mobile application that allows keyless entry by entering pin codes directly on the door lock. It also provides a log of who unlocked the door during what time. It also can creates pin codes for guests and have scheduled codes for them. The only downside is that it only acts like a lock, it does not have a door handle. We would like to have our product to be the full set, a door handle along with a lock itself with the same functionality. We also do not know if their product have an emergency pin code that could work when the wifi is down.
    \item \href{https://a.co/d/g1BpVmg}{ULTRALOQ U-Bolt Pro WiFi Smart Lock}. This product has lots of features like fingerprint, keypad, and a physical key to unlock the door. It does provide custom pin code creation, allowing users to share their custom pin codes to guests. It also allows users to unlock their door by walking close to the lock itself. The cons is that it does not have a pin generation feature for the lock, it also does not have an emergency pin code that can help them unlock the lock when the wifi is down.
\end{enumerate}

%% Sustainability Statement %%

\subsection{Sustainability Statement}

In building our smart lock, we are committed to creating a product that is safe, reliable, and long-lasting for everyday users. We prioritize the use of high-quality, durable materials to extend the product’s lifespan and reduce electronic waste. Our design emphasizes energy efficiency and minimal environmental impact throughout the product’s lifecycle.

We aim to make the smart lock accessible by balancing performance with affordability, ensuring that advanced security technology is available to a wide range of users. Social sustainability is also a key concern — our product is designed with inclusivity in mind, offering features that accommodate users of different ages and abilities.

By focusing on durability, responsible material sourcing, and user-centered design, we strive to reduce our environmental footprint while promoting safe and equitable access to smart home security.
