\section{Neena Nguyen}

\subsection{Personas}
I designed a few user personas to represent the type of consumer likely to use or to benefit from the project prototype. 

\subsection{Ethics Statement}
I outlined the ethics statement for our smart lock, taking into consideration responsible design and implementation. I recognized potential risks with things like user privacy and data security to reassure users and recognize their concerns and needs for transparency.

\subsection{Lifecycle Assessment}
I designed a lifecycle assessment for the smart lock to evaluate its environmental impact from sourcing materials to end of life disposal.

\subsection{Understanding ESP32C3 Integration with Firebase}
I read up on documentation for connecting the ESP32C3 to Wi-Fi and Firebase with the goal of exploring how our smart lock would utilize a cloud to authenticate users.

\subsection{Researching Potential Input Method}
I researched for an optimal input method, deciding between a physical keypad or touch interface for the mobile application. I compared past projects to see the components used for physical keypads, thinking about price points and ease of integration. For the touch interface option, I compared the different technologies and web development stacks other people used for a touch interface. 

\subsection{Interim Presentation}
I organized the interim presentation by designing the template on Canva for a clear, professional layout. I structured the speaking roles and allocated the allotted time between roles and topics.